\documentclass[9pt, a4paper]{article}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[parfill]{parskip}

% DejaVu Serif font
\usepackage{DejaVuSerif}
\usepackage[T1]{fontenc}
% Add amssymb for all the math symbols we might need.
\usepackage{amssymb}
\usepackage{amsmath}
% For moving the title up
\usepackage{titling}
\setlength{\droptitle}{-10em}


\pagestyle{fancy}
\fancyhf{}
\lhead{COM-506 - EPFL}
\rhead{Privacy Pass}


\date{2022-04-04}
\title{Privacy Pass: Bypassing Internet Challenges Anonymously\\
\large (COM-506 Report)
}
\author{Majdouline Ait Yahia, Lúcás C. Meier}

\begin{document}

\maketitle

\section*{Abstract}
The internet is full of malicious and spam traffic. Some websites
try to mitigate this through mechanisms like CAPTCHAs, requiring
users to solve puzzles before accessing their site. These websites
use fingerprinting in order to keep track of vetted users. This avoids
a constant need to re-solve puzzles to access websites. On the other hand,
this harms user privacy, through excessive tracking. If users try
and circumvent this tracking through privacy tools like
Tor \cite{tor_2004}, then they're faced with a large amount of puzzles
to solve once again.

This paper \cite{davidson_privacy_2018} addresses the issue by designing
a protocol in which a challenge server can issue tokens to users,
which can later be redeemed to access a site. By issuing multiple
tokens for each challenge solved, the effort of legitimate users
is reduced. To preserve their privacy, the protocol is designed
so that issued tokens can't be linked with redeemed tokens, so
that the activity of users can't be easily tracked.

\section{Background}
\section{Implementation}

\subsection{Core Idea}

The core idea of the scheme is that if you have a PRF

$$
F : K \times X \to Y
$$

Then evaluating $F_k(x)$ should be difficult without knowing $k$. Thus,
we can issue a token by choosing a random $t$, calculating $F_k(t)$,
and then sending that to the user. The user will then present
$(x, y)$ to us later, and we check that $F_k(x) = y$. It should be difficult
for them to forge such a pair without knowing $k$.

One problem is that the issuer decides what the token is, so they
can trivially link the issuance and the usage later on, allowing
them to track users.

To get around this, we need to design a protocol for the user
and the issuer to work together, in order for the user to learn $F_k(x)$,
without learning $k$, and without the issuer learning $x$ or $F_k(x)$ either.
This idea is known as an \textit{Oblivious PRF} (OPRF).

\subsection{More Concretely}

Now, let's go over their implementation of an OPRF.

A long time ago, in a galaxy far far away, there was a cyclic group
$\mathbb{G}$ of prime order $q$, and with generator $G \in \mathbb{G}$,
suitable for use in Cryptography.

\subsubsection{A first go}

The PRF we use is defined as:

$$
\begin{aligned}
&F : \mathbb{F}_q \times \mathbb{G} \to \mathbb{G}\\
&F(k, P) := k \cdot P
\end{aligned}
$$

In English, the issuer take a point $P$, and multiplies it by its
secret scalar $k$.

The protocol for turning this into an OPRF uses the same principle
behind a Diffie-Hellman key-exchange: multiplying by scalars commutes:

\begin{enumerate}
    \item The user generates $T \xleftarrow{R} \mathbb{G}$,
          $r \xleftarrow{R} \mathbb{F}_q$, sets $P \gets r \cdot T$, and sends
          $P$ to the issuer.
    \item The issuer computes $Q \gets k \cdot P$, and sends $Q$ to the user.
    \item The user computes $W \gets \frac{1}{r} \cdot Q$. The pair $(T, W)$ is their token.
\end{enumerate}

Note that $Q = k \cdot P = kr \cdot T$, so $\frac{1}{r} \cdot Q = k \cdot T$,
so our protocol is at least correct.

\subsubsection{Malleability}

One little issue with the scheme as described is that using
a pair $(T, W = k \cdot T)$, a user can calculate another valid pair,
as $(\alpha \cdot T, \alpha \cdot W)$. In other words, the tokens
are malleable.

To get rid of this malleability, we use the oldest trick in the book:
a hash function. We define a hash function $H_1 : \{0, 1\}^\lambda \to \mathbb{G}$.
Instead of picking a random point $T$, we pick a random \textit{seed}
$t \in \{0, 1\}^\lambda$, defining $T := H_1(t)$. Our token then
becomes the pair $(t, W)$, which isn't malleable.

\subsubsection{Using diferent values for $k$}

Another issue with the scheme so far is that nothing stops the issuer
from using different values of $k$ for different users. This would
allow them to link tokens together, because they would be able to tell
which $k$ was used, by virtue of the token being valid for that $k$.

To avoid this, we can require the issuer to commit to a public key
$Y = k \cdot G$ in advance, via some kind of Public-Key-Infrastructure (PKI).

During step 2, the issuer then proves that they used the same $k$, in zero-knowledge:

$$
\Pi(Y, Q, P ; k) := Y = k \cdot G \land Q = k \cdot P
$$

The paper cites a protocol for this ZK proof by Chaum and Pedersen
\cite{chaum_wallet_92}. Maurer generalized this type of proof
to arbitrary one-way group homomorphisms, in \cite{maurer_2009}.
In this case, the homomorphism is $\varphi(x) := (x \cdot G, x \cdot P)$,
and we prove that $\varphi(k) = (Y, Q)$ in zero-knowledge. This is
the same type of proof as in the ubiquitous Schnorr signature \cite{schnorr_1990}.

\subsubsection{Batching}

It would be convenient to issue multiple tokens at the same time,
which would allow us to reduce the number of puzzles users have to solve.
We can do this straightforwardly by having the user generate
multiple seeds $t_i$, send multiple points $P_i$, and receive multiple points
$Q_i$ in return. The zero-knowledge proof that the same $k$ was used
is still necessary, and can also be repeated multiple times. These
proofs can also be combined into a more efficient \text{batch proof},
as described in \cite{henry_13}, and explained in the paper. This reduces
communication cost.

\subsection{Redemption}

We've described how to issue tokens, but not how to use those
tokens to request content. The idea is that given a token $(t, W)$,
hashing this token with a hash function $H_2$ allows us to derive
a shared key $K := H_2(t, W)$ with the issuer. The issuer can derive this
key from just $t$, since $W$ satisfies $W = k \cdot H_1(t)$, and the
issuer knows $k$.

The user can then redeem their token $(t, W)$ to access some content $R$
by sending $(t, \text{MAC}_K(R))$ to the issuer, who can then recalculate
$K$ from $t$, and check that $\text{MAC}_K(R')$ is the same, using
the content $R'$ they're responding with. Binding the
request to the content $R$ in a way the server can recompute
avoids potential issues with someone intercepting a token
redemption protocol, and using that to access content.
The issuer must also keep a list of tokens $t$ it has seen, in order
to prevent users from reusing tokens.

\section{Security Notions}

There are two sides to consider when it comes to the security
of this scheme: the issuer, and the user.

The issuer doesn't want users to be able to generate new tokens
without its approval: the tokens should be \emph{unforgeable}.
This is denoted as "One-More-Token" security. This notion
can be modeled as a game, where an adversary runs the protocol,
receiving $N$ tokens, and then attempts to forge an $(N+1)$th token.
Naturally, an adversary should only succeed at this with negligeable
probability.

The user, on the other hand, doesn't want the issuer to link their
tokens together. The essence here is that what the issuer sees
in the redemption phase is independent from what they've seen
in the issuance phase. This can also be modeled as a game, in which
the user runs two signing phases with the adversary, and then
redeems the tokens from one of the two signing phases, with
the adversary then guessing which of the phases the tokens came from.
An adversary should only guess correctly with negligeable probability.

\section{Potential Problems}

\subsection{Monkey in the middle}

A lazy adversary could intercept communication between a user and
the issuer, in order to avoid solving puzzles themselves. They
would receive a puzzle from the issuer, but then forward that puzzle
to the user, pretending to be the adversary. Using the user's response,
they would receive the tokens, instead of the user.

\subsection{Accumulating Tokens}

Since the tokens are unlinkable,
and users are presumably anonymous to the issuer, a user can solve
many puzzles, accumulating a lot of tokens. They can then redeem
these tokens, or even share them with many bots, and conduct
a denial-of-service attack on the whatever service uses the tokens
to restrict spam.

One of the mitigations suggested in the paper is to rotate the $k$
value used in the OPRF, and thus the public key, which invalidates
all tokens created with that $k$. Rotating keys often enough
prevents tokens from being accumulated, to a certain extent.

\subsection{Weakness in small numbers}

Tokens can't be linked with each-other, which makes it difficult
to distinguish users making use of the token protocol from eachother.
Unfortunately, if few users are using the token protocol at all,
there might be enough metadata to link them again. Malicious issuers
might even aggravate the situation by intentionally only issuing
a small number of tokens in total, or rotating the $k$ value excessively
often.

\subsection{Key Rotation}

The paper briefly mentions rotating the $k$ value. This changes
the public key $Y$. Because of this, users need to be aware of
what public key(s) the issuer currently accepts. The paper briefly
mentions having the issuer send the user a list of public keys they accept:
this is a bit silly, because the issuer can then send each user
a different list of public keys, making the tokens linkable. What the
authors most likely meant was having the issuer publicly post
their keys via some kind of PKI, which would ensure all users would
be seeing the same result.

\bibliographystyle{alpha}
\footnotesize \bibliography{bib}
\end{document}
